### 2021-04-08 papers/SYRCoSE/regmachine-eventstruct.tex

\begin{definition}[Covering]
  Let $\leqslant$ be a partial order. 
  Then $\lessdot$ is covering relation \wrt $\leqslant$ whenever 
  $x \lessdot y$ is true if and only if $x < y$ and 
  there is no $z$ \sth $x < z$ and $z < y$.
  A (non-deterministic) function $f : A \fun \pwset{A}$ is a covering function if
  its corresponding relation, \ie ${\frel{f} \defeq \set{\tup{x, y} ~|~ y \in f(x)}}$, 
  is a covering relation.
\end{definition}

>>>>

\begin{definition}[Covering]
  Let $\leqslant$ be a partial order. 
  Then $\lessdot$ is covering relation \wrt $\leqslant$ whenever 
  $x \lessdot y$ is true if and only if $x < y$ and 
  there is no $z$ \sth $x < z$ and $z < y$.
  A (non-deterministic) function $f$ from $A$ to the set of finite subsets of $A$ is a covering function if
  its corresponding relation, \ie ${\frel{f} \defeq \set{\tup{x, y} ~|~ y \in f(x)}}$, 
  is a covering relation.
\end{definition}
